Supplementary Materials for cILR: Taxonomic enrichment analysis with isometric log ratios

### 2021-07-26 supplemental.tex

\section{Distribution of p-values}

>>>>

\section{Distribution of p-values}
We also demonstrate the validity our inference procedure by assessing the distribution of p-values. We used simulated data sets as described in the main manuscript, under different data sparsity levels (0, 0.6) and inter-taxa correlation within the set ($\rho$ = 0, 0.5). We evaluated p-values of the correlation adjusted method for $\rho = 0.5$ case and the p-values of the unadjusted method for $\rho = 0$ case.
